Cybercrime and Online Video Games

### 2019-12-13 paper/paper.tex
Update paper.tex
sandboxing + corrected bib

\usepackage{graphicx}

@@

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
 	\centering
	\includegraphics[width = .4\linewidth]{ThreadCount.png}
	\caption{Thread Count}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
 	\centering
	\includegraphics[width=.4\linewidth]{CommentCount.png}
	\caption{Comment Count}
\end{subfigure}
\caption{Thread and Comment Pie Charts}
\end{figure}

@@

@@

>>>>

\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
 	\centering
	\includegraphics[width = .4\linewidth]{ThreadCount.png}
	\caption{Thread Count}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
 	\centering
	\includegraphics[width=.4\linewidth]{CommentCount.png}
	\caption{Comment Count}
\end{subfigure}
\caption{Thread and Comment Pie Charts}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width = .5\linewidth]{DylanProduct.png}
	\caption{Dylan's Product Advertisement}
\end{figure}

@@

\subsubsection{Sandboxing}
Sandboxing reffers, in security, to a mechanism that allows you to separate running programs.
This prevents most vulnerabilities from spreading throught the system.
Since it is often used on unested or untrusted code, code injection can't propagate
and thus can't work, preventing the cheat from ever working in the first place. 
This also allows the commpany to avoid banning players since the cheats don't work.
